Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-03-17 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Madrzy_Thesis: update ch 6

The results are presented for each of the four burner positions and each of the three fuels.  For the natural gas fueled experiments only two replicates were conducted at each position given the high level of control and repeatability.  For the gasoline and polyurethane fueled experiments, three replicates were conducted at each position.  The results of the wall temperatures and heat fluxes are presented as averages of the replicate experiments.  The measures of the fire including heat release rate and flame/plume temperatures were also recorded to ensure consistency with the data presented in the previous section.

@@

@@

>>>>

The results are presented for each of the four burner positions, (0.61~m, 0.31~m, 0.15~m and 0.0~m), and each of the three fuels in Appendix X.  For the natural gas fueled experiments only two replicates were conducted at each position given the high level of control and repeatability.  For the gasoline and polyurethane fueled experiments, three replicates were conducted at each position. The position is measured as the distance between the edge of the burner closest to the wall and the wall.  The results of the wall temperatures and heat fluxes are presented as averages of the replicate experiments.  In the sections below, examples of the averaged data from the gasoline fueled experiments will be presented to demonstrate the impact on distance on the conditions measured on the wall. Then a composite graph of the measured thermal impacts on the wall versus distance will be shown for each fuel type.

@@

Figure~\ref{IW_SC_TWGAS} shows the temperatures of the array of thermocouples located along the vertical centerline of the gasoline fueled burner.  The beads of the thermocouples were installed in the wall and were flush with the wall surface. In each graph, the average temperature of the replicate experiments, for each thermocouple position is shown.  Moving the burner from

\begin{figure}[p]
	\centering
	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0_61m_RepsAvg}
	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0_31m_RepsAvg}\\ 
	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0_15m_RepsAvg}
	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0m_RepsAvg}\\	
	\caption[Wall Temperatures along the centerline of the gasoline fueled burner]{Wall Temperatures along the centerline of the gasoline fueled burner.  The temperatures are averages of three replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top left position and moving from left to right the distances are 0.61~m, 0.31~m,0.15~m,and 0~m.}
	\label{IW_SC_TWGAS}
\end{figure}

@@

Figure~\ref{IW_SC_TWGAS} relabelshows the temperatures of the array of thermocouples located along the vertical centerline of the gasoline fueled burner.  The beads of the thermocouples were installed in the wall and were flush with the wall surface. In each graph, the average temperature of the replicate experiments, for each thermocouple position is shown.  Moving the burner from

\begin{figure}[p]
	\centering
	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0_61m_RepsAvg}
	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0_31m_RepsAvg}\\ 
	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0_15m_RepsAvg}
	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0m_RepsAvg}\\	
	\caption[Wall Temperatures along the centerline of the gasoline fueled burner]{Wall Temperatures along the centerline of the gasoline fueled burner.  The temperatures are averages of three replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top left position and moving from left to right the distances are 0.61~m, 0.31~m,0.15~m,and 0~m.}
	\label{IW_SC_TWGAS}
\end{figure}
